---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# randseq

randseq is a package for the programming language R in development for the 
analysis of randomness in sequences of distinct options (e.g., numbers or 
letters). randseq can help you determine with several of indices how systematic 
a sequence of options is according to different benchmarks of randomness. Its 
focus lies on the detection of patterns that are typically found in human 
generated sequences.

## Installation

Once accepted (!), you can install the released version of randseq from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("randseq")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("TImA97/randseq")
```
## Getting started

This is quick guide is meant to show you the indices of randomness that can be 
computed with randseq. As of now, randseq offers 15 different indices of
randomness that can be easily computed as can be seen in the following example:

All functions take as first argument a vector (your random sequence). In most
cases you also have to specify the number of possible `options` a sequence can 
contain. The following index indicates how regular a sequence is with a 
value of 0 indicating no regularity and a value of 1 maximum regularity. 

```{r}
library(randseq)

reg_index(c(1,2,1,2,1,1,2,2,2), 2)
```

The `options`argument is important because many indices will reflect the fact
that one or several options were omitted in a sequence. 
Let's take the example from above, but assume this time that there are 
three possible options, i.e., one option was completely omitted!

```{r}
reg_index(c(1,2,1,2,1,1,2,2,2), 3)
```

As you can see, the resulting index is now higher, indicating increased regularity.

Some indices have additional arguments or do not have the `options`argument. 
More information and examples on how to use all indices can be found in the
documentation. 


## All-inclusive option

If you want all available indices or a list of indices of your choice to be 
computed, you can use the `all_rand()` function. This function will by default
return all indices of randomness for a given `vector` or `data.frame` (in the latter
case indices are computed using a row-wise format). 

Let's take the example from above again, but this time call the `all_rand()`
function:

```{r}
round(all_rand(c(1,2,1,2,1,1,2,2,2), options = 2), 2)
```

But you can also explicitely specify the indices that should be computed:

```{r}
all_rand(c(1,2,1,2,1,1,2,2,2), options = 2, indices = c("reg_index", "rng_index"))
```

You can just enter all relevant arguments into the `all_rand()` function and
it will take care of everything else and insert your specified arguments
in the right places! 


## List of randomness indices

The following list contains all indices that are implemented in randseq.
More indices may be added in the future. 

- digram_rep
- repetitions
- series
- cluster_ratio
- null_score
- reg_index
- runs_index
- coupon_score
- gap_score
- poker_score
- rng_index
- rng2_index
- tp_index
- redundancy_index
- var_digits

Details on how to use these algorithms can be found in the documentation by entering
`?index_name`into your R-console. 

## References 

The indices implemented in this package are based on the following publications: 

Towse, J.N., Neil, D. Analyzing human random generation behavior: A review of
methods used and a computer program for describing performance. Behavior
Research Methods, Instruments, & Computers 30, 583–591 (1998).
https://doi.org/10.3758/BF03209475

Ginsburg N, Karpiuk P. Random Generation: Analysis of the Responses.
Perceptual and Motor Skills. 1994;79(3):1059-1067.
https://doi.org/10.2466/pms.1994.79.3.1059

Skliar, Osvaldo, Ricardo E. Monge, Guillermo Oviedo, and Víctor Medina. 2009.
Indices of regularity and indices of randomness for m-ary strings.
https://doi.org/10.15517/rmta.v16i1.1418

